One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2024-10-30 paper.tex
update fake abundance estimates

Presenting independent quantiles jointly in a single image is risky.  These caveats make the map difficult to use for most non-statistically trained audiences and even trained statisticians may misinterpret these quantile maps.  To demonstrate the possible consequences of this we (incorrectly) treat the lower and upper quantile plots as though they are intensity functions and integrate them to obtain an expected abundance estimate of approximately 2,800 for the 0.025 quantile map and 10,200 for the 0.975 quantile map.  A naive (and tempting) interpretation of these numbers is as lower and upper limits of the 95\% credible interval for abundance. However, these abundance estimates are not supported by the posterior for abundance (\autoref{fig:realized-abundance-posterior}).  This shows that the tendency to interpret these maps as showing possible intensity surfaces can lead to interpretations that are inconsistent with the very model that generated the maps.

>>>>

Presenting independent quantiles jointly in a single image is risky.  These caveats make the map difficult to use for most non-statistically trained audiences and even trained statisticians may misinterpret these quantile maps.  To demonstrate the possible consequences of this we (incorrectly) treat the lower and upper quantile plots as though they are intensity functions and integrate them to obtain an expected abundance estimate of approximately 2,900 for the 0.025 quantile map and 10,700 for the 0.975 quantile map.  A naive (and tempting) interpretation of these numbers is as lower and upper limits of the 95\% credible interval for abundance. However, these abundance estimates are not supported by the posterior for abundance (\autoref{fig:realized-abundance-posterior}).  This shows that the tendency to interpret these maps as showing possible intensity surfaces can lead to interpretations that are inconsistent with the very model that generated the maps.
